### 2025-06-05 conteudo/background/linux.tex
some work from 04-06

\begin{figure}
\includegraphics[scale=0.25]{diff_command}
\caption{Example of \textit{diff} command executed}
File 1's content is shown in red, and file 2's content is shown in green. \textit{-} 
represents a line that only exists in file 1, \textit{+} represents a line that only 
exists in file 2,\textit{!} represents a line that exists in both files but has modifications 
between them, and empty at the start of a line represents that the line exists in 
both files without any modifications.
\label{fig:diff}
\end{figure}

>>>>

\begin{figure}
\includegraphics[scale=0.25]{diff_command}
\caption[Example of \textit{diff} command executed]{
Example of \textit{diff} command executed
\footnote{
File 1's content is shown in red, and file 2's content is shown in green. \textit{-} 
represents a line that only exists in file 1, \textit{+} represents a line that only 
exists in file 2,\textit{!} represents a line that exists in both files but has modifications 
between them, and empty at the start of a line represents that the line exists in 
both files without any modifications.
}
}
\label{fig:diff}
\end{figure}

### 2025-06-05 conteudo/methods/methods.tex
some work from 04-06

The first method evaluates the proposed tool using an approach from the literature, 
comparing it against the BigCloneBench dataset \citep{bigclonebench}. 
The second method is an empirical analysis of a subset of functions within the 
AMD Display driver that our tool identified as duplicates. After completing these two 
methods, we triangulated the findings to analyze the results comprehensively. 
We chose triangulation because relying solely on the literature-based method has 
limitations and may may be unreliable \citep{bigfail, litreview}. 
As a reminder, all research approaches were done using the text similarity method 
as the code duplication method of the tool.

@@

\begin{itemize}
\item \textbf{Duplicated function pair 1}
\begin{itemize}
\item Function named \textit{offset\_to\_id} in file \textit{dc/gpio/dcn32/hw\_translate\_dcn32.c}.
\item Function \textit{offset\_to\_id} in file \textit{dc/gpio/dcn315/hw\_translate\_dcn315.c}.
\end{itemize}
\item \textbf{Duplicated function pair 2}
%\begin{itemize}
\item Function named \textit{phy\_id\_to\_atom} in file \textit{dc/bios/dce110/command\_table\_helper\_dce110.c}.
\item Function named \textit{phy\_id\_to\_atom} in file \textit{dc/bios/dce60/command\_table\_helper\_dce60.c}.
%\end{itemize}
\end{itemize}

@@

For each duplicated function pair, for each function in the pair, we used the \textit{function information} functionality 
(described in Section \ref{subsec:functioncommand}) to locate all duplications of the function in the codebase, 
as it may have been duplicated more times than the two occurrences of the duplicated function pair. 
This strategy resulted in a collection of duplicated functions and corresponding code files.

@@

For the first alternative, one of the teaching assistants used the ArKanjo tool in the IIO subsystem 
and listed interesting duplicated function pairs that the groups could mitigate this specific 
duplication pair. It is up to the students to refactor the code to mitigate the duplications and 
pass through the process of sending patches to the IIO maintainers for review. For the second 
alternative, we propose a similar experience to the participant observation method, where the 
students pass through the whole process of executing the ArKanjo tool in the AMD display driver, 
analyze the duplications found, create a patch to mitigate a duplication, and send the patch to the 
AMD display driver’s maintainers.

>>>>

The first method evaluates the proposed tool using an approach from the literature, 
comparing it against the BigCloneBench dataset \citep{bigclonebench}. 
The second method is an empirical analysis of a subset of functions within the 
AMD Display driver that our tool identified as duplicates. After completing these two 
methods, we triangulated the findings to analyze the results comprehensively. 
We chose triangulation because relying solely on the literature-based method has 
limitations and may be unreliable \citep{bigfail, litreview}. 
As a reminder, all research approaches were done using the text similarity method 
as the code duplication detection method of the tool.

@@

\begin{itemize}
\item \textbf{Duplicated function pair 1}
\begin{itemize}
\item Function named \textit{offset\_to\_id} in file \textit{dc/gpio/dcn32/hw\_translate\_dcn32.c}.
\item Function named \textit{offset\_to\_id} in file \textit{dc/gpio/dcn315/hw\_translate\_dcn315.c}.
\end{itemize}
\item \textbf{Duplicated function pair 2}
%\begin{itemize}
\item Function named \textit{phy\_id\_to\_atom} in file \textit{dc/bios/dce110/command\_table\_helper\_dce110.c}.
\item Function named \textit{phy\_id\_to\_atom} in file \textit{dc/bios/dce60/command\_table\_helper\_dce60.c}.
%\end{itemize}
\end{itemize}

@@

For each duplicated function pair, for each function in the pair, we used the \textit{function information} functionality 
(described in Section \ref{subsec:functioncommand}) to locate all duplications of the function in the codebase, 
as it may have been duplicated more times than the two occurrences contained in the duplicated function pair. 
This strategy resulted in a collection of duplicated functions and corresponding code files.

@@

For the first alternative, one of the teaching assistants used the ArKanjo tool in the IIO subsystem 
and listed duplicated function pairs found using the text similarity duplication detection method with 
a 90\% similarity threshold. It is then up to the students to refactor the code to mitigate these 
duplications and go through the process of sending patches to the IIO maintainers for review.

For the second alternative, we propose a similar experience to the participant observation method. 
In this approach, students go through the entire process of executing the ArKanjo tool in the 
AMD display driver, analyzing the duplications found, creating a patch to mitigate a duplication, 
and sending the patch to the AMD display driver’s maintainers.

### 2025-06-05 conteudo/results/students.tex
some work from 04-06

Appendix \ref{app:stuart} has references to the artifacts discussed in this section, 
including the duplication function pairs that students mitigate, the students’ reports, 
the patch students sent to the Linux kernel, and the answers to the questionnaire asked 
of the students who worked in the AMD Display driver and the teaching assistant that used 
the tool to find duplications in the IIO subsystem.

@@

Table \ref{tab:stu} summarizes students' groups' mitigation approaches regarding lines 
changed and refactor methods used. Seven groups applied the parameterized refactor method, 
and two applied the extractor method to their approaches to mitigate the duplications. 
The other three groups do not use any refactor methods presented in the literature. 
We discuss the groups' approaches and the subsystem maintainers' opinions on the patches 
that students sent.

@@

Groups three, six, and ten created a struct to encapsulate the parameters and mitigate duplication 
when applying the parameterized method. Group three sent the mitigation to the maintainers and 
approved it without significant comments. In contrast, the patch from group ten was rejected by 
the same maintainer who approved the patch from group three. The maintainer justification to reject 
the patch is that group ten refactored code files that has simple context, threfore adding a layer 
of abstraction to remove a duplication deacrease the code readability without clear gains on 
the codebase quality.

Groups seven and eight used the extract method to approach the mitigations. Group eight sent the 
mitigations to the maintainers, and the code changes were approved, with minor requested changes 
in code style and smaller errors fixed. For group seven mitigation, the maintainers reject their 
patch because the code changes add layers of abstractions to the code, making it more complex and 
challenging to read. The maintainers proposed that group seven remove the duplicated functions and 
insert the duplicated code multiple times where the functions were being called. This suggestion 
may be bad practice for code quality, as it adds more complexity and responsibility to a bigger 
function; it is viewed as the best choice for removing layers of abstraction and making the 
code easier to read.

>>>>

Appendix \ref{app:stuart} has references to the artifacts discussed in this section, 
including the duplication function pairs that students mitigate, the students’ reports, 
the patch students sent to the Linux kernel, and the answers to the survey asked 
of the student who worked in the AMD Display driver and the teaching assistant that used 
the tool to find duplications in the IIO subsystem.

@@

Table \ref{tab:stu} summarizes students' groups' mitigation approaches regarding lines 
changed and refactor methods used. Seven groups applied the parameterized refactor method, 
and two applied the extractor method to their approaches to mitigate the duplications. 
The other three groups do not use any refactor methods presented in the literature.

@@

Groups three, six, and ten created a struct to encapsulate the parameters and mitigate duplication 
when applying the parameterized method. Group three sent the mitigation to the maintainers and 
approved it without significant comments. In contrast, the patch from group ten was rejected by 
the same maintainer who approved the patch from group three. The maintainer justification to reject 
the patch is that group ten refactored code files that has simple context, threfore adding a layer 
of abstraction to remove a duplication deacrease the code readability without clear gains on 
the codebase quality. Figure \ref{fig:group_10_reply} shows the maintainers's feedback for group ten.

\begin{figure}
\includegraphics[scale=0.8]{group_10_reply}
\caption[Maintainers' Feedback on Group Ten's Patch]{
Maintainers' Feedback on Group Ten's Patch
\footnote{Image obtained from Linux Lore, which is publicly provided at:
\url{https://lore.kernel.org/linux-iio/20250428034222.318898-1-gabrielgeraldinosouza@gmail.com/T/\#u}}
}
\label{fig:group_10_reply}
\end{figure}

Groups seven and eight used the extract method to approach the mitigations. Group eight sent the 
mitigations to the maintainers, and the code changes were approved, with minor requested changes 
in code style and smaller errors fixed. For group seven mitigation, the maintainers reject their 
patch because the code changes add layers of abstractions to the code, making it more complex and 
challenging to read. The maintainers proposed that group seven remove the duplicated functions and 
insert the duplicated code multiple times where the functions were being called. This suggestion 
may be bad practice for code quality, as it adds more complexity and responsibility to a bigger 
function; it is viewed as the best choice for removing layers of abstraction and making the 
code easier to read. Figure \ref{fig:group_7_reply} shows the maintainers's feedback for group seven.

\begin{figure}
\includegraphics[scale=0.8]{group_7_reply}
\caption[Maintainers' Feedback on Group Seven's Patch]{
Maintainers' Feedback on Group Seven's Patch
\footnote{Image obtained from Linux Lore, which is publicly provided at:
\url{https://lore.kernel.org/linux-iio/20250428132551.176788-1-bellacaselli20@gmail.com/}}
}
\label{fig:group_7_reply}
\end{figure}

### 2025-06-05 conteudo/results/table_students.tex
some work from 04-06

1 & IIO & 7 & 14 & None \\ \hline
2 & IIO & 23 & 24 & Parameterize method \\ \hline
3 & IIO & 12 & 30 & Parameterize method \\ \hline
4 & IIO & 2 & 7 & None \\ \hline
5 & IIO & 17 & 70 & Parameterize method \\ \hline
6 & IIO & - & - & Parameterize method \\ \hline
7 & IIO & 21 & 22  & None \\ \hline
8 & IIO & - & - & None \\ \hline
9 & IIO & 33 & 52 & Parameterize method \\ \hline
10 & IIO & 32 & 58 & Parameterize method \\ \hline
11 & IIO & - & - & Parameterize method \\ \hline
12 & AMD & 89 & 489 & None \\ \hline

\hline
\end{tabular}
\caption{Refactor methods used and metrics of the students's mitigations.}
\label{tab:stu}
\end{table}

>>>>

1 & IIO & 7 & 14 & None \\ \hline
2 & IIO & 23 & 24 & Parameterize method \\ \hline
3 & IIO & 12 & 30 & Parameterize method \\ \hline
4 & IIO & 2 & 7 & None \\ \hline
5 & IIO & 17 & 70 & Parameterize method \\ \hline
6 & IIO & - & - & Parameterize method \\ \hline
7 & IIO & 21 & 22  & Extract method \\ \hline
8 & IIO & 20 & 16 & Extract method \\ \hline
9 & IIO & 33 & 52 & Parameterize method \\ \hline
10 & IIO & 32 & 58 & Parameterize method \\ \hline
11 & IIO & - & - & Parameterize method \\ \hline
12 & AMD & 89 & 489 & None \\ \hline

\hline
\end{tabular}
Lines with \textit{-} represents groups that does not provided the Linux Lore URL of the PATCH sent to consult.
\caption{Refactor methods used and metrics of the students's mitigations.}
\label{tab:stu}
\end{table}
